---
title: "p8105_hw2_hn2339"
author: "Haowei Ni"
date: "2018/9/30"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
```

#Question 1 
```{r}
NYC_Subway <- read_csv("data /NYC_Subway.csv") %>%
  # clean the name to lower case 
  janitor::clean_names() %>%
  # remove the unwante columns 
  select(-division, -exit_only, -staffing, -staff_hours, -free_crossover, -north_south_street, -east_west_street, -corner, -station_location, -entrance_location, -entrance_longitude, -entrance_latitude) %>%
  # convert the entry variable from "YES NO" to "TRUE FALSE"
  mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE)) 
```
There are totally 20 variables in this data set. Retain line, statation name, station longitude/latitude, route1~11, entrance type, entry, vending and ADA compliance. Step 1 is change the capital letter to lower case. Step 2 is remove all the unwanted columns. Step 3 is change the entry variable (YES or NO) to logical variable (TRUE or FLASE). The data is not tidy yet. 
```{r}
 #find the distinct station, . keep_all = TRUE keep all other data 
distinct_station = distinct(NYC_Subway, station_name, line, route1, .keep_all = TRUE) 
   dim(distinct_station)
#
ADA_compliant = filter(distinct_station, ada == TRUE)
   dim(ADA_compliant)
Without_vending = filter(distinct_station, vending == "NO", entry == TRUE)
   dim(Without_vending)
Without_vending_no = filter(distinct_station, vending == "NO")
   dim(Without_vending_no)
```
There are totally 450 distinct stations both by name and by line. 
There are totally 75 stations are ADA compliant. 
The proportion is 5/9 = 55.6%
```{r}
reformat_data = gather(NYC_Subway, key = route_number, value =route_name, route1:route11 )
   distinct_AA = distinct(reformat_data, station_name, line, route_name, .keep_all = TRUE) 
   distinct_A = filter(distinct_AA, route_name == "A")
   dim(distinct_A) 
ADA = filter(distinct_A, ada == TRUE)
   dim(ADA) 
```
There are totally 60 stations. 
There are 17 ADA compliant.

#Question 2 
```{r}
library(readxl)
Mr_TrashWheel = read_excel("data /HealthyHarborWaterWheelTotals2017-9-26.xlsx", range = "A2:N258") %>%
  janitor::clean_names() %>%
  filter(!is.na(dumpster)) %>%
  mutate(sports_balls = as.integer(round(sports_balls, 0)))
  Mr_2016 = filter(Mr_TrashWheel, year == 2016)
```

```{r}
library(readxl)
Precipation_2016 = read_excel("data /HealthyHarborWaterWheelTotals2017-9-26.xlsx", sheet = 4, range = "A2:B15") %>%
  janitor::clean_names() %>%
  filter(!is.na(total)) %>%
  mutate(Year = "2016")
Precipation_2017 = read_excel("data /HealthyHarborWaterWheelTotals2017-9-26.xlsx", sheet = 3, range = "A2:B15") %>%
  janitor::clean_names() %>%
  filter(!is.na(total)) %>%
  mutate(Year = "2017")
Precipation = bind_rows(Precipation_2016, Precipation_2017) %>%
  mutate(month = month.name[month])
  P2017 = filter(Precipation, Year == 2017)
```
The dimension of the Mr_TrashWheel is `r dim(Mr_TrashWheel)`. There are total 14 variables. Dumpster, volumes and weight, homes powered and other kinds of trashes are the key variables. 
The dimension of the Precipation is `r dim(Precipation)` There are total 3 variables. Month, total precipation and year. 
The median number of sports balls in a dumpster in 2016 is `r median(Mr_2016$sports_balls)`
The total precipation in 2017 is `r sum(P2017$total)`
#Question 3 
```{r}
# install.packages("devtools")
devtools::install_github("p8105/p8105.datasets")
```

```{r}
library(p8105.datasets)
    data(brfss_smart2010) 
    BRFSS = janitor::clean_names(brfss_smart2010) %>%
    filter(topic == "Overall Health") %>%
    select(-c(class, topic, question, sample_size, confidence_limit_low:geo_location)) %>%
    spread(key = response, value = data_value) 
    Scatter_plot = filter(BRFSS, locationdesc == "NY - New York Country" | locationdesc == "NY - Queens Country")
    destination = distinct(BRFSS, locationdesc, .keep_all = TRUE) 
    state = distinct(BRFSS, locationabbr, .keep_all = TRUE)
    most = tail(names(sort(table(BRFSS$locationabbr))), 1)
    Excellent_2002 = filter(BRFSS, year == "2002") %>%
    # 
    mutate(proportion = (Excellent + `Very good` ) / (Excellent + Fair + Good + Poor + `Very good`))
#make the histogram 
    ggplot(Excellent_2002, aes(x = Excellent)) +
      geom_histogram()
#make the scatterplot 
    Scatter = filter(BRFSS, locationdesc == "NY - New York County" | locationdesc == "NY - Queens County")
    ggplot(Scatter, aes(x = year, y = Excellent)) + 
      geom_point(aes(color = locationdesc), alpha = 0.5)
```
The number of unique destination is `r nrow(destination)`. 
The number of unique state is `r nrow(state)`. So every state is represented. 
The most state which observed most is `r most`. 
The median of 2002 excellent is `r median(Excellent_2002$Excellent, na.rm = TRUE)`


